---
title: "Shopify  Data science Challenge"
author: "Taiwo Owoseni"
date: "May 9th 2022"
output:
  pdf_document: default
  html_notebook: default
subtitle: AOV 
---

```{r}
plot(cars)
```

### **Question**

Given some sample data, write a program to answer the following:[ click here to access the required data set](https://docs.google.com/spreadsheets/d/16i38oonuX1y1g7C_UAmiK9GkY7cS-64DfiDMNiR41LM/edit#gid=0)

On Shopify, we have exactly 100 sneaker shops, and each of these shops sells only one model of shoe. We want to do some analysis of the average order value (AOV). When we look at orders data over a 30 day window, we naively calculate an AOV of \$3145.13. Given that we know these shops are selling sneakers, a relatively affordable item, something seems wrong with our analysis. 

1.  Think about what could be going wrong with our calculation. Think about a better way to evaluate this data. 

2.  What metric would you report for this dataset?

3.  What is its value?

### Approach

*Here are the list of steps I intend to use to evaluate if the AOV is a good measurement or not:*

-   **Investigating the data set** : Look for outliers and Visually understand the data

-   **Better way to evaluate the data** : Apply Monte Carol to simulate the more than 100 dataset (10,000 in stead)

-   **Try other metric:** CLV

-   **Compare the metrics using Hypothesis** : ANOVA or Repeated Measures Analysis

### **Load Data**

```{r}

```
